---
title: "World Happiness Report"
author: "Koki Ando"
date: "4/03/2018"
output:
  html_document:
    code_folding: hide
    highlight: tango
    number_section: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
This time our team at USYD analyzes World Happiness Report.

# Preparation
## Packages
```{r}
library(data.table)
library(tidyverse)
library(corrplot)
library(plotly)
library(wildcard)
library(shiny)
library(PerformanceAnalytics)
library(DT)
```

## Data Importing & Cleaning
```{r}
setwd("/Users/KokiAndo/Desktop/R/R report/World Happiness")
#(https://www.kaggle.com/unsdsn/world-happiness)
wh15 <- fread("2015.csv", data.table = FALSE)
wh16 <- fread("2016.csv", data.table = FALSE)
wh17 <- fread("2017.csv", data.table = FALSE)
wh15$year <- 2015
wh16$year <- 2016
wh17$year <- 2017

names(wh17)[2] <- "Happiness Rank"
names(wh17)[3] <- "Happiness Score"
names(wh17)[6] <- "Economy (GDP per Capita)"
names(wh17)[8] <- "Health (Life Expectancy)"
names(wh17)[11] <- "Trust (Government Corruption)"
names(wh17)[12] <- "Dystopia Residual"

wh15_17 <- bind_rows(wh15,wh16,wh17)
names(wh15_17)[5] <- "SD_error"
wh15_17 <- wh15_17 %>% select(Country:year,-Region, -SD_error)

names(wh15_17) <- c("Country","Happiness_Rank","Happiness_Score","Economy_GDP",
                 "Family","Health","Freedom","Trust",
                 "Generosity","Dystopia_Residual","year")
```

## Data Components
```{r}
names(wh15_17)
head(wh15_17)
str(wh15_17)
summary(wh15_17)
```


# Countries that did not appear in 3 years in a row
```{r}
test <- wh15_17 %>% group_by(Country) %>% mutate(count = sum(year))
test %>% filter(count != 6048) %>% select(Country, Happiness_Rank, year) %>% arrange(Country)
```


# Analysis
## Correlation
### Correlation check No.1
What makes nations happy?
```{r}
corrplot(cor(wh15_17 %>% 
               select(Happiness_Score:Dystopia_Residual)), 
         method="color",  
         sig.level = 0.01, insig = "blank",
         addCoef.col = "black", 
         tl.srt=45, 
         type="upper"
         )
```



## Histogram
```{r}
happiness17 <- subset(wh15_17, year == 2017)
hist(wh15_17$Happiness_Score)
```

## Ranking
```{r}
p <- ggplot(wh15_17 %>% filter(year==2017), aes(x= Happiness_Score,y= 
                                             reorder(Country,Happiness_Score))) + 
  geom_point(colour = "red", alpha = .5) + 
  geom_segment(aes(yend=reorder(Country, Happiness_Score)), xend = 0, colour="pink", alpha = .5) + 
  theme(axis.text.y = element_text(angle = 45, hjust = 1)) + 
  labs(title = "World Hapiness Rnak in 2017", y = "Country Name", x = "Hapiness Score")
ggplotly(p)
```

### 2017 Hapiness Score World Map
```{r}
world <- map_data('world')
world <- world %>% filter(region != "Antarctica")
world <- fortify(world)
happiness.score17 <- wh15_17 %>% select(Country, Happiness_Score, year) %>% filter(year == 2017)
happiness.score17 <- wildcard(df = happiness.score17, wildcard = "United States", values = "USA",
         expand = TRUE, rules = NULL)
happiness.score17 <- wildcard(df = happiness.score17, wildcard = "United Kingdom", values = "UK",
         expand = TRUE, rules = NULL)

happiness.score17 <- wildcard(df = happiness.score17, wildcard = "Democratic Republic of the Congo", values = "Congo (Kinshasa)",
         expand = TRUE, rules = NULL)
ggplot() + 
  geom_map(data=world, map=world,
                  aes(x=long, y=lat, group=group, map_id=region),
                  fill="white", colour="black") + 
  geom_map(data=happiness.score17, map=world,
                  aes(fill=Happiness_Score, map_id=Country),
                  colour="black") + 
  scale_fill_continuous(low="red", high="yellow",
                               guide="colorbar") + 
  labs(title = "World Hapiness Score in 2017")
```


## Scatter Plot
### Scatter Plot No.1
```{r}
plot(Happiness_Score ~ Economy_GDP, data = wh15_17)
```


### Scatter Plot No.2
```{r}
plot_ly(data = wh15_17 %>% filter(year == 2017), 
        x=~Economy_GDP, y=~Happiness_Score, type = "scatter",
        text = ~paste("Country:", Country)) %>% 
  layout(title = "Happiness and GDP relationship", 
         xaxis = list(title = "GDP per Capita"),
         yaxis = list(title = "Hapiness Score"))
```
### Scatter Plot No.3

```{r}
plot_ly(data = wh15_17, 
        x=~Economy_GDP, y=~Happiness_Score, color=~Health, type = "scatter",
        text = ~paste("Country:", Country)) %>% 
        layout(title = "Happiness, GDP and Health relationship", 
               xaxis = list(title = "GDP per Capita"),
               yaxis = list(title = "Hapiness Score"))
```


[Reference](https://stackoverflow.com/questions/30706124/ploting-the-world-map-in-r)


[参考](http://gg-hogehoge.hatenablog.com/entry/2013/09/23/212746)
[参考2](http://www.statsoft.org/wp-content/uploads/2016/09/Lecture6_HKMapVis.html)
[参考3](https://www.kaggle.com/swl554/visualizing-happiness-around-the-globe)





## Boxplot
### Happiness score by region(boxplot)
```{r}
names(wh16)[4] <- "Happiness_Score"
ggplot(wh16, aes(x=Region, y= Happiness_Score, colour = Region)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Happiness Score Boxplot",
       x = "Region",
       y = "Happiness Score")
```

## Extract & Compare Top5, Middle5 and Worst5 Countries
```{r}
world.happiness17 <- wh15_17 %>% filter(year == 2017)
top5 <- world.happiness17 %>% head(5) %>% mutate(Level = "TOP5")
middle5 <- world.happiness17[76:80, ] %>% mutate(Level = "MIDDLE5")
worst5 <- world.happiness17 %>% tail(5) %>% mutate(Level = "WORST5")

caomparison <- bind_rows(top5, middle5, worst5)

caomparison$Level <- as.factor(caomparison$Level)
caomparison <- transform(caomparison, Level = factor(Level, levels = c("TOP5", "MIDDLE5", "WORST5" )))
ggplot(caomparison, aes(x = Level, y = Family, fill = Level)) + geom_boxplot()
```

```{r}
datatable(caomparison,
          options = list(
            lengthMenu = c(5, 10, 15)
          ),
          caption = 
            htmltools::tags$caption(
              style = 'caption-side: bottom; text-align: center;', 
              htmltools::em('Data table that only includes top5, middle5 and worst5 countries'))
          )
```

```{R}
caomparison.score <- caomparison %>% gather(key = "columns", value = "score", Happiness_Score:Dystopia_Residual)
caomparison.score %>% 
  ggplot(aes(x = Level, y = score, colour = Level, fill = Level)) + 
  geom_boxplot(position=position_dodge(width=1)) + facet_wrap(~columns, scales = "free")
```

